% interacttfssample.tex
% v1.05 - August 2017

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled
%\setlength\bibindent{2em}% To increase hanging indent in bibliography when line spacing is doubled

% \usepackage[numbers,sort&compress]{natbib}% Citation support using natbib.sty
% \bibpunct[, ]{[}{]}{,}{n}{,}{,}% Citation support using natbib.sty
% \renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

\usepackage{natbib}
\usepackage{xcolor}

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\begin{document}

\articletype{ARTICLE TEMPLATE}% Specify the article type or omit as appropriate

\title{Characterizing AI-generated partisan news articles through computational text analysis}

\author{
\name{Anonymous Author(s)}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK}
}

\maketitle

\begin{abstract}
The rise of Large Language Models and 
\end{abstract}

\begin{keywords}
; lists; figures; tables; mathematics; fonts; references; appendices
\end{keywords}


\section{Introduction}
This is a test \citet{baly2020we} test

\section{Literature Review}


\subsection{AI in journalism}

AI has been dragging the attention of the journalism community for the past years. As such, the definition of AI in journalism has been evolving \colorbox{pink}{citation needed}

\begin{itemize}
  % \item RQ 1: How does the language of AI-generated news articles differ from human-written news articles?
  \item RQ 1: How does AI generate news articles when only the headline of partisan news is provided? (Fully AI-generated scenario)
  \begin{itemize}
    \item RQ 1.1: What do AI generate for quotes in news articles?
    \item RQ 1.2: Who are the entities mentioned in AI-generated news articles?
    \item RQ 1.3: Do AI-generated news articles present more partisan bias compared to human-written news articles?
  \end{itemize}
\end{itemize}

\subsection{Rising human-AI collaboration}

The lack of transparency in AI systems raises concerns about the potential biases in AI-generated content \colorbox{pink}{citation needed}. 

\begin{itemize}
  \item RQ 2: How does AI complete news articles when only the headline of partisan news and the portion of the human-written article is provided? (Human-AI collaboration scenario)
  \begin{itemize}
    \item RQ 2.1: How does AI generate the quotes in news articles when there is a quote in the human-written article?
    \item RQ 2.2: How does AI generate the entities mentioned in news articles when there are entities mentioned in the human-written article?
    \item RQ 2.3: Do AI-generated news articles with the portion of human-written article present more partisan bias compared to human-written news articles?
  \end{itemize}
\end{itemize}

\begin{itemize}
  \item RQ 3: How does AI generate news articles when the headline of partisan news and the name of the media outlet is provided? (Human-AI collaboration scenario)
  \begin{itemize}
    \item RQ 3.1: How does AI generate the quotes in news articles when there is a quote in the human-written article?
    \item RQ 3.2: How does AI generate the entities mentioned in news articles when there are entities mentioned in the human-written article?
    \item RQ 3.3: Do AI-generated news articles with the name of the news outlet present more partisan bias compared to human-written news articles?
  \end{itemize}
\end{itemize}

\bibliographystyle{apalike}
\bibliography{bibliography}

\end{document}
